% % % Beginning of preamble...
\documentclass[10pt,a4paper]{report}

% % % packages to be used...
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lineno}
\usepackage{subfig}
\usepackage{caption}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{float}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{datetime}
\usepackage{nameref}
\usepackage{ragged2e}
\usepackage{enumitem}
\usepackage[left=2.50cm, right=2.50cm, top=2.50cm, bottom=2.50cm]{geometry}
\usepackage{hyperref}

% % % hiperref options
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

% % % Additional tex files to include:
\include{StylesDefinitions}

% % % definitions...
\newcommand{\me}{Yasiel Delabat Díaz}

\newcommand{\supervisor}{Dr. Claire A. David}

\newcommand{\qttitle}{Infrared tests on the ATLAS thermomechanical petal prototype built at DESY.}

\newcommand{\qtabstract}{In order to take advantage of the High Luminosity LHC (HL-LHC) by 2025, the ATLAS detector will undergo the Phase-II upgrade, which will include a new Inner Tracker (ITk) consisting of a pixel detector close to the beam line and a strip detector surrounding it. The strip detector has two endcaps composed  by 6 disks perpendicular to the beam axis with 32 petals arranged radially around them. Petals are the local support structures holding the ATLAS end-cap ITk strip sensors. \\
This report details the infrared measurements on the thermomechanical petal prototype of the ATLAS end-cap strip detector performed using a customized thermal chamber built at DESY where a CO$_{2}$ cooling system is used in order to reach temperatures of around -25\space$^\circ $C. High emissivity electric tape was extensively used to correct the input from infrared camera and allowing more accurate quantitative measurements of the Silicon surface temperature.
Preliminary comparisons with FEA simulations showed fairly similar behaviour with respect to the measurements performed on both sides of the petal. 
In addition, this report explores the feasibility of using a less invasive computer-based method to calibrate the temperature provided by the infrared camera.}

\newcommand{\draft}{DRAFT}

\newcommand{\version}{v0.4}

% % % Show line numbers (for DRAFT version)
\linenumbers

% % % New table columns alignment option:
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

% % % new command to repeat a character N times:
\makeatletter
\newcount\my@repeat@count
\newcommand{\myrepeat}[2]{%
  \begingroup
  \my@repeat@count=\z@
  \@whilenum\my@repeat@count<#1\do{#2\advance\my@repeat@count\@ne}%
  \endgroup
}
\makeatother

% % % Command to produce a line of custom length:
\newcommand*{\xdash}[1][3em]{\rule[0.5ex]{#1}{0.55pt}}

% % % Beginning of document...
\begin{document}

	% % % Add the cover page here...
	\input{CoverPage}
	\clearpage	
	
	% % % Add the different parts here...
	% \tableofcontents
	\input{TableOfContent}
	\clearpage
	
	\input{Introduction}
	\clearpage
	
	\input{Chapter01}
	\clearpage
	
	\input{Chapter02}
	\clearpage
	
	\input{Chapter03}
	\clearpage
	
	\input{Chapter04}
	\clearpage
	
	\input{Conclusions}
	\clearpage
	
	\input{References}
	\clearpage
	
\end{document}