% % % Set the style for this file:
\pagestyle{references}

% % % Beginning of the section
\section*{\uppercase{References}}\label{referen}
	\bigskip
	\bigskip
	\begin{enumerate}[label={[\arabic*]}]
	
		\item ATLAS Collaboration, "Technical Design Report for the ATLAS Inner Tracker Strip Detector", Tech. Rep. CERN-LHCC-2017-005. ATLAS-TDR-025, CERN, Geneva, Apr 2017.
		
		\item C. Meola,	\textit{Infrared Thermography Recent Advances and Future Trends}. Bentham Science, New York, 2012.
		
		\item J. R. Howell and R. Siegel, \textit{Thermal Radiation Heat Transfer}. Hemisphere Publishing Co., third ed., 1992.
		
		\item R. Usamentiaga et al., "Infrared Thermography for Temperature Measurement and Non-Destructive Testing.", \textit{Sensors}, vol. 14, pp. 12305-12348, 2014.
		 
		\item S. Chomet and G. Gaussorgues, \textit{Infrared Thermography}. Chapman and Hall, first ed., 1994.
		
		\item K. Moellmannet et al., "Selected critical applications for thermography: Convections in fluids, selective emitters and highly reflecting materials.", \textit{In Proceedings of the Infrared Camera Calibration Conference}, vol. 6, (Las Vegas (NV), USA), pp. 161-173, oct 2015.
		
		\item InfraTec GmbH, Gostritzer Strasse 61-63, \textit{VarioCAM \textregistered\space high resolution user manual}, nov 2015.
		
		\item M. Vollmer and K.-P. Moellmann,	\textit{Infrared Thermal Imaging: Fundamentals, Research and Applications}. Boschstr. 12, 69469 Weinheim, Germany: Wiley-VCH Verlag GmbH, 2010.
		
		\item ASTM E1933-97. "Standard Test Methods for Measuring and Compensating for Emissivity Using Infrared Imaging Radiometers", 1997.
		
		\item ISO 18434-1:2008. "Condition monitoring and diagnostics of machines–Thermography– Part 1: General procedures", 2011.
		
		\item S. Marinetti and P. G. Cesaratto, "Emissivity estimation for accurate quantitative thermography", NDT \& E International, vol. 51, pp. 127-134, oct 2012.
		
		\item B. Sopori et al., "Calculation of emissivity of si wafers", Journal of Eletromagnetic Materials, vol. 28, no. 12, 1999.
		
		\item $[$ Yu-Heng's report on FEA ... $]$
	\end{enumerate}